Capstone Graphs

### 2022-04-27 eda/capstone/capstone-report.Rmd
capstone pres update

# plotting
library(ggplot2)
library(ggpubr)

@@

```{r}
medauf_adj <- medauf %>% 
  filter(label_correct != "none") %>% 
  ggplot(., aes(x=x, y=y, color=as.factor(label_correct), size=Count)) +
  geom_point(alpha=0.6) +
  theme_minimal() +
  guides(size = "none") +
  labs(
    x = "Dimension 2", y = "Dimension 1",
    title = "Adjusted Medical Org Arguments (pro)",
    color = "Argument"
  )
medauf_adj
```

```{r}
ggsave("medauf_adj.png",medauf_adj,height = 4, width = 6)
```

>>>>

# plotting
library(ggplot2)
library(ggpubr)
#library(extrafont)
#font_import()
#loadfonts(device = "all")

library(showtext)
font_add_google(name = "Quattrocento Sans")

@@

```{r}
# turn on showtext

```

```{r}
showtext_auto()
medauf_adj <- medauf %>% 
  filter(label_correct != "none", label_correct != "Violence Against Abortion Seekers") %>%
  mutate(Count = Count) %>% 
  ggplot(., aes(x=x, y=y, color=as.factor(label_correct), size=Count)) +
  geom_point(alpha=0.6) +
  theme_minimal() +
  guides(size = "none",
         color=guide_legend(nrow=3, byrow=TRUE)) +
  labs(
    x = "Dimension 2", y = "Dimension 1",
    title = "Medical Organizations' Arguments (Proponents)",
    color = "Argument"
  ) +
  theme(legend.title=element_text(size=16, family = "Quattrocento Sans"),
        legend.text=element_text(size=16, family = "Quattrocento Sans"),
        legend.position="bottom", legend.direction="vertical",
        title = element_text(size=14, family = "Quattrocento Sans"),
        axis.text = element_text(size=12, family = "Quattrocento Sans"),
        axis.title = element_text(size=12, family = "Quattrocento Sans"))
medauf_adj
```

```{r}
ggsave("medauf_adj.png",medauf_adj,height = 7, width = 9)
```
